Incentivizing Exploration with Unbiased History

### 2018-10-16 algg.tex
stuff

\swedit{Before we describe our algorithms, we will first analyze a
  simple policy \ALGG that fully discloses the history over all
  previous rounds, and lets the agents make the ``greedy'' choices
  across all rounds. Even though the algorithm does not guarantee low
  regret, it will be used as a subroutine in our main algorithms.  In
  particular, we show that because of the randomness in the rewards,
  with constant probability, $\ALGG$ will incentivize the agents to
  play each arm at least once.}

\begin{lemma}
\label{lem:greedy}
Under \Cref{ass:embehave}, there exist two constants $\GdT = O_K(1)$
and $\GdP = \Omega_K(1)$ such that for any arm $a$, with probability
at least $\GdP$, \ALGG of $\GdT$ rounds pulls this arm at least
once.\footnote{The notations $O_k$ and $\Omega_K$ hide the dependence
  on the number of arms $K$.}
\end{lemma}

\begin{proof}
  Set $\GdT = (K-1) \cdot c_T + 1$ and $\GdP = (1/3)^{\GdT}$. We fix
  the behavior of agents in $\GdT$ rounds and consider the case that
  all realized rewards in $\GdT$ rounds are 0.

In this case, we want to show that arm $a$ is pulled at least once. We prove by contradiction. Suppose arm $a$ is not pulled. By averaging argument, we know that there is some other arm $a'$ which is pulled at least $c_T + 1$ rounds. Suppose in round $t$, arm $a'$ is pulled exactly $c_T + 1$ times. By Assumption \ref{ass:embehave}, we know 
\[
\hat{\mu}_{a'}^t \leq 0 + c_m / \sqrt{c_T} < 1/3. 
\]
On the other hand, we have $\hat{\mu}_a^t \geq 1/3 > \hat{\mu}_{a'}^t$. This contradicts with the fact that in round $t$, arm $a'$ is pulled.

In addition, we know that this case happens with probability at least
$(1/3)^{\GdT} = \GdP$ as each arm's mean is at most $2/3$. To sum up,
we know that with probability at least $\GdP$, \ALGG of $\GdT$ rounds
pulls arm $a$ at least once.
\end{proof}
%%% Local Variables:
%%% mode: latex
%%% TeX-master: "main"
%%% End:

>>>>

\swedit{Before we describe our algorithms, we will first analyze a
  simple policy \ALGG that fully discloses the history over all
  previous rounds, and lets the agents make the ``greedy'' choices
  across all rounds. Even though the algorithm does not guarantee low
  regret, it will be used as a subroutine in our main algorithms.  In
  particular, we show that because of the randomness in the rewards,
  with constant probability, \ALGG will incentivize the agents to
  play each arm at least once.}

\begin{lemma}
\label{lem:greedy}
Under Assumption \ref{ass:embehave}, there exist two constants $\GdT = O_K(1)$
and $\GdP = \Omega_K(1)$ such that for any arm $a$, with probability
at least $\GdP$, \ALGG of $\GdT$ rounds pulls this arm at least
once.\footnote{The notations $O_k$ and $\Omega_K$ hide the dependence
  on the number of arms $K$.}
\end{lemma}

\begin{proof}
  Fix any arm $a$. Let $\GdT = (K-1) \cdot c_T + 1$ and
  $\GdP = (1/3)^{\GdT}$. \swedit{We will condition on the event that
    all realized rewards in $\GdT$ rounds are 0, which occurs with
    probability at least $\GdP$ under Assumption~\ref{ass:embehave}.}
  In this case, we want to show that arm $a$ is pulled at least
  once. We prove by contradiction. Suppose arm $a$ is not pulled. By
  the pigeonhole principle, we know that there is some other arm $a'$
  that is pulled at least $c_T + 1$ rounds. Let $t$ be the round in
  which arm $a'$ is pulled exactly $c_T + 1$ times. By Assumption
  \ref{ass:embehave}, we know
  \[
    \hat{\mu}_{a'}^t \leq 0 + c_m / \sqrt{c_T} < 1/3. 
  \]
  On the other hand, we have
  $\hat{\mu}_a^t \geq 1/3 > \hat{\mu}_{a'}^t$. This contradicts with
  the fact that in round $t$, arm $a'$ is pulled, instead of arm $a$.
  \swdelete{ In addition, we know that this case happens with
    probability at least $(1/3)^{\GdT} = \GdP$ as each arm's mean is
    at most $2/3$. To sum up, we know that with probability at least
    $\GdP$, \ALGG of $\GdT$ rounds pulls arm $a$ at least once.}
\end{proof}
%%% Local Variables:
%%% mode: latex
%%% TeX-master: "main"
%%% End:
